---
title: "Detection of brain cancer using genome-wide cell-free DNA fragmentation profiles and repeat landscapes"
author: ""
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    keep_md: yes
---

The current repository contains the analysis source code for the manuscript on brain cancer detection using genome-wide cell-free DNA by Mathios et al. It is structured following the workflowr framework, where it can be built to generate report pages including all the figures and code.

Here is an overview of the directory structure:

* analysis: This directory includes analysis scripts in Rmarkdown format that can be run to generate the paper figures.

* code: This directory includes the code for training and evaluating the ARTEMIS-DELFI model, and performing the DECIFER analyis.

* data: This path includes the raw data used as input to the analysis performed in the study.

* docs: The html reports in this directory are generated by compiling the Rmarkdown files in the analysis directory. 

* output: This directory includes the results from training the ARTEMIS-DELFI model, and running the decifer analysis as R objects or text files.

To reproduce the figures and tables in Mathios et al.

```{r mathios, eval=FALSE}
wflow_build("analysis/*.Rmd")
```


```{r publish, eval=FALSE, eval = FALSE}
wflow_publish("analysis/*.Rmd")
```
